---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))


```{r, eval=FALSE}
library(vifcopula)
datagen_gauss <- fcopsim(t_max = 1000, n_max = 100, family = 1)

datagen <- datagen_gauss
data <- list(u = datagen$u, 
             n_max = datagen$n_max, 
             n_group = n_group, 
             t_max = datagen$t_max, 
             k_max = datagen$k_max, 
             gid = datagen$gid, 
             structfactor = datagen$structfactor)
init <- list(copula_type = datagen$family, 
             v = datagen$v, 
             par = datagen$theta, 
             par2 = datagen$theta2)
other <- list(seed = 126, core = 8, iter = 1000, 
              n_monte_carlo_grad = 1, n_monte_carlo_elbo = 10, 
              eval_elbo = 100, adapt_bool = T, adapt_val = 1, 
              adapt_iterations = 50, tol_rel_obj = 0.1)
vi_gauss <- vifcopula::vifcop(data,init,other)

plot(datagen$v, vi_gauss$mean_iv[1:t_max])
abline(a= 0, b=1, col="red")
plot(datagen$theta, vi_gauss$mean_iv[(t_max+1):(t_max+n_max)])
abline(a= 0, b=1, col="red")
```

```{rcpp}
 Data input : Checked
 Core : 8
 General setting : Checked
 Init hyperparams : Checked
Begin eta adaptation.
Iteration:   1 / 250 [  0%]  (Adaptation)
Iteration:  50 / 250 [ 20%]  (Adaptation)
Iteration: 100 / 250 [ 40%]  (Adaptation)
Iteration: 150 / 250 [ 60%]  (Adaptation)
Iteration: 200 / 250 [ 80%]  (Adaptation)
Success! Found best value [eta = 1] earlier than expected.

Begin stochastic gradient ascent.
  iter       ELBO   delta_ELBO_mean   delta_ELBO_med   notes 
   100      3e+04             1.000            1.000
   200      3e+04             0.510            1.000
   300      3e+04             0.340            0.019   MEDIAN ELBO CONVERGED

Drawing a sample of size 1000 from the approximate posterior... 
COMPLETED.
It took 9.9482 seconds.
```

```{r, eval=FALSE}
datagen_student <- fcopsim(t_max = 1000, n_max = 100, family = 2)
datagen <- datagen_student
data <- list(u = datagen$u, 
             n_max = datagen$n_max, 
             n_group = n_group, 
             t_max = datagen$t_max, 
             k_max = datagen$k_max, 
             gid = datagen$gid, 
             structfactor = datagen$structfactor)
init <- list(copula_type = datagen$family, 
             v = datagen$v, 
             par = datagen$theta, 
             par2 = datagen$theta2)
other <- list(seed = 126, core = 8, iter = 1000, 
              n_monte_carlo_grad = 1, n_monte_carlo_elbo = 10, 
              eval_elbo = 100, adapt_bool = T, adapt_val = 1, 
              adapt_iterations = 50, tol_rel_obj = 0.1)
vi_student <- vifcopula::vifcop(data,init,other)

plot(datagen$v, vi_student$mean_iv[1:t_max])
abline(a= 0, b=1, col="red")
plot(datagen$theta, vi_student$mean_iv[seq(from = t_max+1, to = t_max+2*n_max, by = 2 )])
plot(datagen$theta2, vi_student$mean_iv[seq(from = t_max+2, to = t_max+n_max, by = 2 )])
abline(a= 0, b=1, col="red")
```

```{r, eval=FALSE}
datagen_clayton <- fcopsim(t_max = 1000, n_max = 100, family = 3)
datagen <- datagen_clayton
data <- list(u = datagen$u, 
             n_max = datagen$n_max, 
             n_group = n_group, 
             t_max = datagen$t_max, 
             k_max = datagen$k_max, 
             gid = datagen$gid, 
             structfactor = datagen$structfactor)
init <- list(copula_type = datagen$family, 
             v = datagen$v, 
             par = datagen$theta, 
             par2 = datagen$theta2)
other <- list(seed = 126, core = 8, iter = 1000, 
              n_monte_carlo_grad = 1, n_monte_carlo_elbo = 10, 
              eval_elbo = 100, adapt_bool = T, adapt_val = 1, 
              adapt_iterations = 50, tol_rel_obj = 0.1)
vi_clayton <- vifcopula::vifcop(data,init,other)

plot(datagen$v, vi_clayton$mean_iv[1:t_max])
abline(a= 0, b=1, col="red")
plot(datagen$theta, vi_clayton$mean_iv[(t_max+1):(t_max+n_max)])
abline(a= 0, b=1, col="red")
```

```{r, eval=FALSE}
datagen_gumbel <- fcopsim(t_max = 1000, n_max = 100, family = 4)
datagen <- datagen_gumbel
data <- list(u = datagen$u, 
             n_max = datagen$n_max, 
             n_group = n_group, 
             t_max = datagen$t_max, 
             k_max = datagen$k_max, 
             gid = datagen$gid, 
             structfactor = datagen$structfactor)
init <- list(copula_type = datagen$family, 
             v = datagen$v, 
             par = datagen$theta, 
             par2 = datagen$theta2)
other <- list(seed = 126, core = 8, iter = 1000, 
              n_monte_carlo_grad = 1, n_monte_carlo_elbo = 10, 
              eval_elbo = 100, adapt_bool = T, adapt_val = 1, 
              adapt_iterations = 50, tol_rel_obj = 0.1)
vi_gumbel <- vifcopula::vifcop(data,init,other)

plot(datagen$v, vi_gumbel$mean_iv[1:t_max])
abline(a= 0, b=1, col="red")
plot(datagen$theta, vi_gumbel$mean_iv[(t_max+1):(t_max+n_max)])
abline(a= 0, b=1, col="red")
```


```{r, eval=FALSE}
datagen_frank <- fcopsim(t_max = 1000, n_max = 100, family = 5)
datagen <- datagen_frank
data <- list(u = datagen$u, 
             n_max = datagen$n_max, 
             n_group = n_group, 
             t_max = datagen$t_max, 
             k_max = datagen$k_max, 
             gid = datagen$gid, 
             structfactor = datagen$structfactor)
init <- list(copula_type = datagen$family, 
             v = datagen$v, 
             par = datagen$theta, 
             par2 = datagen$theta2)
other <- list(seed = 126, core = 8, iter = 1000, 
              n_monte_carlo_grad = 1, n_monte_carlo_elbo = 10, 
              eval_elbo = 100, adapt_bool = T, adapt_val = 1, 
              adapt_iterations = 50, tol_rel_obj = 0.1)
vi_frank <- vifcopula::vifcop(data,init,other)

plot(datagen$v, vi_frank$mean_iv[1:t_max])
abline(a= 0, b=1, col="red")
plot(datagen$theta, vi_frank$mean_iv[(t_max+1):(t_max+n_max)])
abline(a= 0, b=1, col="red")
```

```{r, eval=FALSE}
datagen_joe <- fcopsim(t_max = 1000, n_max = 100, family = 6)
datagen <- datagen_joe
data <- list(u = datagen$u, 
             n_max = datagen$n_max, 
             n_group = n_group, 
             t_max = datagen$t_max, 
             k_max = datagen$k_max, 
             gid = datagen$gid, 
             structfactor = datagen$structfactor)
init <- list(copula_type = datagen$family, 
             v = datagen$v, 
             par = datagen$theta, 
             par2 = datagen$theta2)
other <- list(seed = 126, core = 8, iter = 1000, 
              n_monte_carlo_grad = 1, n_monte_carlo_elbo = 10, 
              eval_elbo = 100, adapt_bool = T, adapt_val = 1, 
              adapt_iterations = 50, tol_rel_obj = 0.1)
vi_joe <- vifcopula::vifcop(data,init,other)

plot(datagen$v, vi_joe$mean_iv[1:t_max])
abline(a= 0, b=1, col="red")
plot(datagen$theta, vi_joe$mean_iv[(t_max+1):(t_max+n_max)])
abline(a= 0, b=1, col="red")
```


```{r, eval=FALSE}
copfamily = matrix(sample(c(1,3,4,5,6),size = 100, replace = T),ncol=1)
datagen_mix <- fcopsim(t_max = 1000, n_max = 100, family = copfamily)
datagen <- datagen_mix
data <- list(u = datagen$u, 
             n_max = datagen$n_max, 
             n_group = n_group, 
             t_max = datagen$t_max, 
             k_max = datagen$k_max, 
             gid = datagen$gid, 
             structfactor = datagen$structfactor)
init <- list(copula_type = datagen$family, 
             v = datagen$v, 
             par = datagen$theta, 
             par2 = datagen$theta2)
other <- list(seed = 126, core = 8, iter = 1000, 
              n_monte_carlo_grad = 1, n_monte_carlo_elbo = 10, 
              eval_elbo = 100, adapt_bool = T, adapt_val = 1, 
              adapt_iterations = 50, tol_rel_obj = 0.1)
vi_mix <- vifcopula::vifcop(data,init,other)

plot(datagen$v, vi_mix$mean_iv[1:t_max])
abline(a= 0, b=1, col="red")
plot(datagen$theta, vi_mix$mean_iv[(t_max+1):(t_max+n_max)])
abline(a= 0, b=1, col="red")
```
